Neural Neural Textures Make Better Simulators ``I Can't Believe It's Not Real!''

### 2022-06-13 CORL/example.tex
Replaced batch size 'B' with batch size 'N'

\newcommand{\toB}{_{1\dots B}}
% \newcommand{\toBL}{_{1\dots B,\text{ } 1\dots L}}
\newcommand{\toBL}{_{1\dots B, 1\dots L}}
\newcommand{\toL}{_{1\dots L}}

@@

\begin{figure}[H]
	\begin{center}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
		\includegraphics[width=400pt]{../images/main_diagram_beautiful.pdf}
	\end{center}
	\caption{
		% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
		% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		% $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		%
		%JUNE 12:
		%Don't say 4 main components; say 2 components and 2 losses
		%TODO: Try to use right-angled arrows
		%TODO: Use tau as a function
		%Copy paste the figure multiple times, deleting things
		%Mention "Neural Neural Texture": Its a function mapping UV to RGB
		%Formulation doesnt mentino texture; just uvl inputs and final outputs
		%Always use function notation tau(u,v) instead of just tau (in figure as well) 
		%The arrow should be running through tau. It's not a variable its a function...
		%Rename 'B' to "N" for batch size
		%Figure 8: Align consistent with inconsistent and use all 5 green ones
		%
		This figure is an overview TRITON.
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses.
		Although $\pi\toB$ and $\ph\toB$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

@@

%THIS WILL BE REPLACED BY SUMMARY SECTION
% 	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\pi_{1\dots B}$. This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.

@@

	Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $B$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene. 
	\begin{equation}
		u\toBL=\text{unproject}(\ph\toB,s\toB)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_B
	\end{equation}

	To maintain surface consistency, we sample a random batch of UVL scenes $S\toB$, and translate them into $\ph\toB$.
	Using geometric knowledge of the scene encoded in $S\toB$, we individually unproject each $\ph_i \in \ph\toB$ back into texture space, to obtain $B$ sets of $L$ unprojected textures $u\toBL$.
	We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toBL)\toL$.
	This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.

@@

	As it turns out, $\lTR$ is sufficient to ensure surface consistency without $\lUC$, though using both yields better results than either one alone. 
	For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.
	There are some advantages to using $\lTR$ alone though: when just using $\lTR$ you can use batch sizes as small as $B=1$, allowing you to save video memory. 
	Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch.

>>>>

\newcommand{\toN}{_{1\dots N}}
% \newcommand{\toNL}{_{1\dots B,\text{ } 1\dots L}}
\newcommand{\toNL}{_{1\dots N, 1\dots L}}
\newcommand{\toL}{_{1\dots L}}

@@

\begin{figure}[H]
	\begin{center}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
		\includegraphics[width=400pt]{../images/main_diagram_beautiful.pdf}
	\end{center}
	\caption{
		% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
		% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		% $N$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		%
		%JUNE 12:
		%Don't say 4 main components; say 2 components and 2 losses
		%TODO: Try to use right-angled arrows
		%TODO: Use tau as a function
		%Copy paste the figure multiple times, deleting things
		%Mention "Neural Neural Texture": Its a function mapping UV to RGB
		%Formulation doesnt mentino texture; just uvl inputs and final outputs
		%Always use function notation tau(u,v) instead of just tau (in figure as well) 
		%The arrow should be running through tau. It's not a variable its a function...
		%Rename 'B' to "N" for batch size
		%Figure 8: Align consistent with inconsistent and use all 5 green ones
		%
		This figure is an overview TRITON.
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses.
		Although $\pi\toN$ and $\ph\toN$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

@@

%THIS WILL BE REPLACED BY SUMMARY SECTION
% 	Given a batch of $N$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\pi_{1\dots B}$. This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.

@@

	Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $N$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene. 
	\begin{equation}
		u\toNL=\text{unproject}(\ph\toN,s\toN)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_N
	\end{equation}

	To maintain surface consistency, we sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
	Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph_i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
	We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toNL)\toL$.
	This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.

@@

	As it turns out, $\lTR$ is sufficient to ensure surface consistency without $\lUC$, though using both yields better results than either one alone. 
	For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.
	There are some advantages to using $\lTR$ alone though: when just using $\lTR$ you can use batch sizes as small as $N=1$, allowing you to save video memory. 
	Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch.
